Generating Hubbard Model Solutions from Anderson Impurity Model Solutions

### 2021-08-24 notes.tex
minor edits

@@

	\includegraphics[width=0.8\textwidth]{dimer_bath.png}
	\caption{The process of symmetrizing the Rg fixed point Hamiltonian and then creating a dimer+bath Hamiltonian.}

@@

We  can thus obtain a family of Hamiltonians \(\tilde H^D(i,j)\) obtained by setting \(0\) and \(1\) by setting the two sites of the dimer to any nearest-neighbour \(i,j\) on the lattice and the effective bath to the rest \(N-2\) sites of the lattice. We will then create the the entire Hubbard Hamiltonian by combining the members of this family of Hamiltonians according to a prescription which is guided by the symmetries of the problem.
However, we first specify the two approximations made along the entire journey from the original Hubbard model to the reconstructed one:
	\item We then perform a unitary RG on $H^A$. This leads to a fixed-point Hamiltonian $\mathcal{U}_A H^A \mathcal{U}_A^\dagger$. At this point, we go from the fixed point Hamiltonian to the dimer+bath Hamiltonian: $H^D = Z\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right] Z^{-1}$. This constitutes the second approximations we make. This constitutes the second approximations we make.
We now tile the real-space lattice with this Hubbard dimer Hamiltonian to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H = T\left[ H^{D} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the dimer Hamiltonian to span the target real-space lattice. We quote the final form of $\tilde H$ here to explain what the tiling means, but the explanation is given in a later section.

@@

	\tilde H = - \frac{2t^D}{Nw}\sum_{\sigma \left<ij \right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{2U^D}{N}\sum_i \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)

@@

What that means is that we have placed the Hubbard dimer at all nearest neighbour pairs to reconstruct a new Hubbard model. If we assume that the tiling mostly rectifies the explicit symmetry-breaking made while choosing the auxiliary system as well as taking the zero mode, we can write

@@

%The content of the above equation is that we expect the final tiled translationally invariant new (renormalised) Hubbard Hamiltonian to be connected to the bare parent Hubbard model through some unitary/similarity transformation $\mathcal{U}$.
The existence of $U$ is contingent on how good the approximations are, and strictly speaking needs to be verified.

@@

The local Hamiltonians look like

@@

	H^D_{i,j} = H^D(i, j) -t^A\sum_{k \in \text{NN of i}}\left(c^\dagger_{i\sigma}c_{k\sigma} + \text{h.c.}\right)-t^A\sum_{k \in \text{NN of j}}\left(c^\dagger_{j\sigma}c_{k\sigma} + \text{h.c.}\right) - t^A\sum_{\left<k,q\right> \neq i,j}\left(c^\dagger_{j\sigma}c_{k\sigma} + \text{h.c.}\right)

>>>>

	\label{dimer_p_bat}
	\tilde H^D = H^D(0,1) - t^D \sum_{\vec k}^\text{eff. bath}\left(c^\dagger_{0\sigma}c_{\vec k,\sigma} + c^\dagger_{1\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath}\epsilon_{\vec k}\hat n_{\vec k}

@@

	\includegraphics[width=0.3\textwidth]{dimer_bath.png}
	\caption{The process of symmetrizing the Rg fixed point Hamiltonian and then creating a dimer+bath Hamiltonian. We first add the asymmetric Hamiltonians to get a symmetrized Hamiltonian. In the symmetrized Hamiltonian, the dimer has \(w\) entry points into the bath, \(w\) being the coordination number of the lattice. We then merge these \(w\) lattice sites (enclosed in the black box) into a single lattice site.}

@@

We  can thus obtain a family of Hamiltonians \(\tilde H^D(i,j)\) obtained by setting \(0\) and \(1\) by setting the two sites of the dimer to any nearest-neighbour \(i,j\) on the lattice and the effective bath to the rest \(N-2\) sites of the lattice. The next step in the programme is to tile the real-space lattice with this dimer+bath Hamiltonian \(\tilde H_D\) to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H = T\left[ \tilde H^{D} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the dimer Hamiltonian to span the target real-space lattice. We quote the final form of $\tilde H$ here to explain what the tiling means, but the explanation is given in a later section.

@@

	\color{red}{\tilde H = - \frac{2t^D}{Nw}\sum_{\sigma \left<ij \right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{2U^D}{N}\sum_i \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)}

@@

What that means is that we have placed the Hubbard dimer at all nearest neighbour pairs to reconstruct a new Hubbard model. If we assume that the tiling mostly rectifies the explicit symmetry-breaking made while choosing the auxiliary system as well as dropping the correlation on the bath sites, we can write

@@

The existence of $U$ is contingent on how good the approximations are.
We mention the two approximations made along the entire journey from the original Hubbard model to the reconstructed one here.
	\item We then perform a unitary RG on $H^A$. This leads to a fixed-point Hamiltonian $\mathcal{U}_A H^A \mathcal{U}_A^\dagger$. At this point, we go from the fixed point Hamiltonian to the dimer+bath Hamiltonian in eq.~\ref{dimer_p_bat}. If we represent this transformation from the fixed point Hamiltonian to the Hamiltonian in eq.~\ref{dimer_p_bat} by an operator \(Z\), we can write $H^D = Z\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right] Z^{-1}$. This constitutes the second approximation we make.

@@

We recall the dimer+bath Hamiltonian here, since we are going to create the full Hamiltonian by combining various realizations of that Hamiltonian:

@@

We will first create a "local" Hamiltonian, where one particular nearest neighbour pair \((i,j)\) makes up the dimer sites of the Hamiltonian, while the rest \(N-2\) sites of the lattice make up the effective bath. The zero-mode site of the effective bath is mapped to one of the nearest-neighbours of \(i\) or \(j\)
	\tilde H^D_(i,j) = H^D(i, j) - t^D \sum_{\vec k}^\text{eff. bath (i,j)}\left(c^\dagger_{i\sigma}c_{\vec k,\sigma} + c^\dagger_{0\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath (i,j)}\epsilon_{\vec k}\hat n_{\vec k}
